---
title: "Lab 03 - Nobel laureates"
author: "Hannah Kingham"
date: "`r Sys.Date()`"
output: html_document
---


### Load packages and data

```{r load-packages, message = FALSE, warning=FALSE}
library(tidyverse) 
```

```{r reading-nobel-data, message = FALSE}
nobel <- read_csv("data/nobel.csv")
```

### Exercise 1

#### Narrative
There are 935 observations and 26 different variables. Each row represents a different prize winner (there are duplicate rows if someone won a prize more than once), row represents every prize given out.


### Exercise 2

#### Code

```{r nobel-living}
nobel_living <- nobel %>%
  filter(!is.na(country), 
         !gender %in% "org", 
         is.na(died_date))
  
```

#### Narrative
First filtered observations where country is not NA, then for observations where gender is not org and finally for observations with died date of NA indicating they are still alive.

nobel_living is now a data frame with 228 entries, representing all nobel prize winners that are currently alive people (not organisations) and for whom country data is avaliable.


### Exercise 3

#### Code

```{r facet-bar-plot}
nobel_living <- nobel_living %>%
  mutate(country_us = 
           if_else(
             country == "USA", "USA", "other")
         )
nobel_living_science <- nobel_living %>%
  filter(category %in% c("Physics", 
                         "Chemistry",
                         "Medicine",
                         "Economics")
         )
ggplot(nobel_living_science, 
       mapping = aes(x = country_us)) +
geom_bar()+
  facet_wrap(~category)+
  coord_flip()
```

#### Narrative

This shows very similar results to the buzzfeed article, numbers are not exactly the same but general trends and proportions are.


### Exercise 4

#### Code

```{r born-country-us}
nobel_living_science %>%
  mutate(born_country_us =
           if_else(born_country == 
               "USA", "USA", "other"))%>%
  count(born_country_us)
```
105 of the nobel prize winners were born in the USA while 123 were born elsewhere.

### Exercise 5

#### Narrative

*Remove this text and add your answer here.*

#### Code

```{r facet-bar-plot-redo}
# remove this comment and add your code here
```


### Exercise 6

#### Code

```{r born-country}
# remove this comment and add your code here
```

#### Narrative

*Remove this text and add your answer here.*